### 2019-10-31 letter.tex
aditya comments addressed

A previous version of this paper was submitted to InfoVis 2019. This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to TVCG, please make reference to this  InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}''

The present version of the paper addresses all of the issues mentioned by the reviewers. The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 
\begin{itemize}
    \item[\textbf{C1:}] More clearly articulate the merits over alternative tools, such as Keshif. 
     \item[\textbf{C2:}] Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item[\textbf{C3:}] Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item[\textbf{C4:}] Better justify the choice of tasks in the study. 
     \item[\textbf{C5:}] Explain the choice of the four research questions.
     \item[\textbf{C6:}] Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize} 
We have spent the last four months 
preparing a revised version of this paper.
\agp{One thing that is confusing is that the bulletpoints above
don't neatly map to the bulletpoints below, or the enumerated list after that. Stopped reading after this}
Here, we provide a response to the reviews. 
In our revised submission,
(i) we discuss the merits of having an interface like \noah
integrated within an existing spreadsheet, as opposed
to other general-purpose exploratory tools such as  Keshif (\textbf{C1});
(ii) we justify our design choice surrounding the binning mechanism
while discussing its limitations (\textbf{C2}); 
(iii) we enrich the user study design section further 
by providing justifications for comparing \noah and Excel (\textbf{C3}), 
explaining the choice of quiz tasks (\textbf{C4}), rephrasing our research questions reflecting the purpose of the user study (\textbf{C5}), and reporting the intra-participant differences for the study (\textbf{C6}).
Moreover, to answer the rephrased research questions, we 
have reorganized the results section to highlight key contributions of \noah while explaining participant experiences in using the tool.
The major changes to the paper include:

@@

\item \textit{Merits over other tools} (\textbf{C1}): \saj{In the paper, we have identified the major contribution of \noah as its \emph{design as a general purpose navigation interface}, the concepts of which can be implemented and integrated as a plug-in to any spreadsheet. As spreadsheets have a massive user-base, enhancing the experience surrounding data exploration and formula computation while maintaining the spreadsheet look and feel as much as possible, has the potential to impact a lot of users. As we mentioned earlier, even users of enterprise solutions prefer Excel for direct data manipulation. Therefore, developing a solution to improve the experience with basic operations of such a tool has its merits.}

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): We have explained our choice of the binning mechanism in the context the third design consideration (\emph{DC3}) and can be found under the title ``Why a Multi-granularity Binned Overview'' in Section~\ref{sec:design}. \saj{In brief, we opted for binning to provide a clear and concise representation of the overall data distribution while minimizing user's back and forth movement across multiple screens during navigation.} However, we acknowledge the limitation of this choice for binning categorical data and discuss possible solutions in Section~\ref{sec:discuss}.

\item \textit{Justification of Excel as a Baseline} (\textbf{C2}):
We have provided justification for using Excel over tabular data analysis (TDA) tools a) by highlighting the appeal of spreadsheets in interacting with data even for the users of enterprise solutions (see Section~\ref{sec:intro}), b) by identifying the scope of tasks supported by spreadsheets and the TDA tools (see Section~\ref{sec:usage} and~\ref{sec:related}), c) by explaining that the goal of spreadsheets is to facilitate direct manipulation and arbitrary derivation of the data unlike TDA tools that hide the data while providing summarized statistics (see Section~\ref{sec:related}), and d) by highlighting the importance of addressing the shortcomings of a tool, the user base of which, far exceeds that of the TDA tools (see Section~\ref{sec:study_design}).

\item \textit{Enhancing the user study design} (\textbf{C4, C5}):
We have added additional explanations on the goal of the study while better articulating the research questions, provided a better justification for the choice of the tasks for the study (see Section~\ref{sec:study_design}) and added a detailed discussion on the limitations of the study. \saj{Specifically, we merged a number of research questions that explored how specific features of \noah affected participants' navigation experience into one broad question which explores their overall experience with \noah and its components. Moreover, we have justified the choice of the quiz tasks by a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}, and b) explaining how these tasks can reveal how people may utilize \noah for spreadsheet navigation. Finally, we have identified two limitations of the study , resulting from sample size and the study design, which we justify based on the scope of the study.}

@@

\saj{In addition to the aforementioned changes, we have reorganized Section~\ref{sec:results} to reflect the rephrased research questions while supporting our findings from the study by providing qualitative observations, such as participants' comments and interaction patterns with the \noah. We have explained how different features of \noah affected participants' spreadsheet navigation experience, either positively or negatively. Based on these observations, we have updated Section~\ref{sec:discuss} to include additional limitations of \noah while highlighting future research opportunities.}

>>>>

A previous version of this paper was submitted to InfoVis 2019. This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to TVCG, please make reference to this  InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}'' The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 
\begin{itemize}
    \item[\textbf{C1:}] More clearly articulate the merits over alternative tools, such as Keshif. 
     \item[\textbf{C2:}] Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item[\textbf{C3:}] Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item[\textbf{C4:}] Better justify the choice of tasks in the study. 
     \item[\textbf{C5:}] Explain the choice of the four research questions.
     \item[\textbf{C6:}] Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize} 
We have spent the last four months 
preparing a revised version of this paper. We thank the reviewers and meta-reviewer for their detailed,
constructive feedback. 
We have taken the feedback very seriously in preparing
the revised version, and we believe the paper is substantially
stronger as a result. \newsaj{The revision necessitated a number of updates to the content of each section and are highlighted in teal color. In Section 1, we cited existing work that highlight the widespread adoption of spreadsheets even among users of advanced enterprise solutions, adding further merit to our goal of addressing navigation challenges within spreadsheets. Recent discourse within the visualization community also echoes our sentiment\footnote{https://twitter.com/FILWD/status/1187411664611749888}---instead of designing a new tool that may cater to a small population, we aim to improve user experience with spreadsheet tools boasting more than $700$ million users. Moreover, we augmented the definitions of spreadsheet interactions like scrolling and steering and clearly articulated the challenges of designing a general purpose plug-in for spreadsheets. In Section 2, we defined the scope of tasks supported by spreadsheets guided by existing taxonomy of abstract visualization tasks. We further enhanced our usage scenario by highlighting how different use cases of \noah maps to the scope defined for spreadsheets. In Section 5, we added additional discussions to clearly articulate the difference in the goals of spreadsheets spreadsheets and TDA tools which further justifies choice of Excel, the most widely used spreadsheet tool, as our baseline in the evaluation study. In Section 4, we added further clarification to the third design consideration (\textbf{DC3}). In Section 5, we provided justifications for developing a multi-granularity overview while explaining why we opted for histogram as an overview representation. In Section 6, we further clarified the goals of the evaluation study while rephrasing the research questions to better reflect those goals. We didn't alter our previous research questions, rather grouped a few research questions into a more high level and less ambiguous question. Moreover, we explained our choice of the quiz tasks and discussed three limitations of our study in detail. We revamped Section 7 completely to better reflect our research questions while adding more qualitative observations regarding the user experience with \noah. We also included an additional analysis on the intra-participant differences. In Section 8, we first added a summary of our takeaways from the evaluation study while discussing additional limitations of \noah and future enhancement opportunities. We now discuss how the updates made to all of these sections addressed the changes suggested by the reviewers.}

@@

\item \textit{Merits over other tools} (\textbf{C1}): \saj{In the paper, we have identified the major contribution of \noah as its \emph{design as a general purpose navigation plug-in} to any existing spreadsheet. As spreadsheets have a massive user-base, enhancing exploration and formula computation on large datasets while maintaining the spreadsheet look and feel as much as possible, has the potential to impact a lot of users. Most of these users employ spreadsheets as their primary data management and analysis tool while shunning enterprise solutions with more advanced features. Therefore, our goal is to develop a solution to improve navigation within spreadsheets.}

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): We have explained our choice of the binning mechanism in the context of the third design consideration (\emph{DC3}). This explanation can be found under the title ``Why a Multi-granularity Binned Overview'' in Section~\ref{sec:design}. \saj{In brief, we opted for binning to provide a clear and concise representation of the overall data distribution while minimizing user's back and forth movement across multiple screens during navigation.} However, we acknowledge limitation of this choice for binning categorical data and discuss possible solutions in Section~\ref{sec:discuss} in the context of our user study findings.

\item \textit{Justification of Excel as a Baseline} (\textbf{C2}):
We have provided justification for using Excel over tabular data analysis (TDA) tools a) by highlighting the appeal of spreadsheets among users who shun more advanced enterprise solutions (see Section~\ref{sec:intro}), b) by identifying the scope of tasks supported by spreadsheets and TDA tools (see Section~\ref{sec:usage} and~\ref{sec:related}), c) by explaining that the goal of spreadsheets is to present the raw data as is, amenable to editing, formula computation, and comparison of derived data unlike TDA tools that hide the data while providing summarized statistics (see Section~\ref{sec:related}), and d) by highlighting the importance of addressing the shortcomings of a tool, the user base of which far exceeds that of TDA tools (see Section~\ref{sec:study_design}).

\item \textit{Enhancing the user study design} (\textbf{C4, C5}):
We have added additional explanations regarding the goal of the study while better articulating the research questions, provided a better justification for the choice of the tasks for the study (see Section~\ref{sec:study_design}) and added a detailed discussion on the limitations of the study. \saj{Specifically, we merged a number of research questions that explored how specific features of \noah affected participants' navigation experience into one broad question which explores their overall experience with \noah and its components. Moreover, we have justified the choice of the quiz tasks by a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}), and b) explaining how these tasks can reveal how people may use \noah for spreadsheet navigation. Finally, we have identified two limitations of the study, resulting from the sample size and the study design, which we justify based on the scope of the study.}

@@

\saj{In addition to the aforementioned changes, we have reorganized Section~\ref{sec:results} to reflect the rephrased research questions. Furthermore, we discuss our findings from the study in the context of the research questions by providing qualitative observations, such as participants' comments and interaction patterns with the \noah. We have explained how different features of \noah affected participants' spreadsheet navigation experience, either positively or negatively. Based on these observations, we have updated Section~\ref{sec:discuss} to include additional limitations of \noah while highlighting future research opportunities.}
